\chapter{Corporate Members}
\label{appendix:ekgf-corporate-members}

The corporate members of the \glsfirst{ekgf} currently are\,---\,ordered by join date:

\paragraph{\agnos}
\label{agnos}
\index{company!agnos.ai}
\index{company!agnos.ai!EKG/Platform}

\href{https://agnos.ai}{agnos.ai} is an Enterprise Knowledge Graph consultancy assisting its clients in
their \gls{ekg} journey from strategy to production.

\paragraph{Wizdom}
\label{wizdom}
\index{company!Wizdom}

\href{http://www.wizdom.com/}{Wizdom} is a recognized leader in providing our clients with
innovative process-based business solutions for improving performance.

\paragraph{\stardogcompany}
\label{stardog}
\index{company!Stardog}
\index{company!Stardog!\glsfmtshort{ekg} platform}
\index{triple store!Stardog}

\href{https://www.stardog.com/}{Stardog}, the leading Enterprise Knowledge Graph platform,
turns data into knowledge to power more effective digital transformations.

\paragraph{\ontotext}
\label{ontotext}
\index{company!Ontotext}
\index{company!Ontotext!GraphDB}
\index{triple store!GraphDB}

\href{https://www.ontotext.com/}{Ontotext} is a global leader in enterprise knowledge graph technology
and semantic database engines.

\paragraph{\dataworld}
\label{dataworld}
\index{company!data.world}
\index{triple store!data.world}

\href{https://data.world}{data.world} makes it easy for everyone—not just the "data people"—to get clear, accurate,
fast answers to any business question.

\paragraph{\eccenca}
\label{eccenca}
\index{company!eccenca}
\index{company!eccenca!Corporate Memory}

\href{https://eccenca.com/}{eccenca} is a leading provider of enterprise knowledge graph management
software and solutions.

\paragraph{Global IDs}
\label{globalids}
\index{global ids}
\index{company!Global IDs}

\href{https://www.globalids.com/}{Global IDs} provides software for enterprise information management (EIM).

\paragraph{\cambridgesemantics}
\label{cambridgesemantics}
\index{company!Cambridge Semantics}
\index{company!Cambridge Semantics!Anzo}
\index{triple store!Anzo}

\href{https://www.cambridgesemantics.com/}{Cambridge Semantics} provides Anzo,
the scalable knowledge graph platform for data integration and analytics.




