\section{Identity}\label{sec:ekg-principles-identity}

Any object in the \glsfmtshort{ekg} is identified with at least one \iindex{universally unique}, \iindex{opaque},
permanent and \iindex{web-resolvable} identifier in the form of an \glsfmtshort{iri} for
the \glsfmtshort{ekg} i.e. an \gls{ekg:iri}.

The \gls{ekg:iri} identifier is permanent, will be proliferated across the company's universe (including ecosystem),
and will be used for the expression of facts about the object including relationships between objects.

Additional non-canonical identifiers (and therefore not called \glspl{ekg:iri}) may also be assigned,
and \myuline{they} \myuline{may} be human-readable (i.e. non-opaque), "external" to
the organization's \glsfmtshort{ekg}, more \iindex{transient} and reassignable.

\textit{Resolving} an identifier\index{identifier resolution} can be done in three ways:
\begin{enumerate}
    \item using it in a query submitted or routed via an internet protocol e.q. a "lookup service" that translates
          one or more "features" of a given existing object to an \gls{ekg:iri}.
    \item constructing it via a standardised policy from key components and applying a hash and optionally
          signing it\,---\,where the object represented by the \gls{ekg:iri} may or may not already exist.
    \item constructing it by giving the object an \gls{ekg:iri} based on a random number in case the \gls{ekg} is
          the authoritative source for the given object.
\end{enumerate}

\paragraph{Rationale}

While the semantic web technologies\,---\,like \gls{rdf}\,---\,generally allow for many and varied \glspl{iri},
and this is still encouraged when integrating systems, there is benefit in being able to rely on one canonical
and unchanging one, which can for example make the mapping of identities a many-to-one rather than a many-to-many task.

\paragraph{Implications}

\begin{itemize}
    \item There should be a mapping or service to resolve other names, keys or \glspl{iri} to the \gls{ekg:iri}.
    \item Since it is immutable, the \gls{ekg:iri} will have to be \textit{opaque} i.e. not be a human-readable
          since even human names, company names, customer numbers, Social Security Numbers can change over time.
    \item Objects that already have a well-established \gls{rdf}-compliant and \gls{linked-data} compliant identifier
          may not necessarily need an additional \gls{ekg:iri}.
          In fact, they may already have one that is external to the company's \gls{ekg}.
          It is in many cases recommended to even give those well-established objects from well-established external
          datasets a company \gls{ekg:iri}. Examples of such objects are \glspl{lei} and \glspl{figi}.
          The \gls{ekgf} will maintain a list of these for convenience.
    \item The use of multiple identities generally means that an \gls{ekg} should \textit{not}
          use the \gls{una} (where use of a different identifier would imply a different object).
          However the \gls{una} \textit{would} apply specifically to the \gls{ekg:iri},
          and this should be ensured by any service.
\end{itemize}
  
