\section{Meaning}\label{sec:ekg-principle-meaning}

The meaning of every \gls{data-point} must be directly resolvable
to a machine-readable mathematical definition.

A \gls{data-point} combines an object\,---\,using its \gls{ekg:iri} as its identifier\,---\,with the value
of a \textit{property} in some context.
Hence data is expressed at its most granular level for both data at rest and data in motion.

The property itself is always an \gls{iri}, often called "predicate-IRI", that refers to an object\footnote{%
    the official term in the \gls{rdf} standard for this object is "resource"%
} that represents "the meaning" of the given \gls{data-point}.
This object has its own identity and is defined through further properties
based on logic that allow information to be rigorously combined, queried and inferred.
These properties that define properties\,---\,also called "axioms"\,---\,are standardized by means of the \glsfirst{owl2}
by the \gls{w3c} and are grouped into \textit{"OWL ontologies"} for management purposes.

% JAG>PER I don't think the sentence below is useful or makes sense...
%However the machine-readable logic does not replace natural language definitions that
%link the properties and statements to the real world.

\paragraph{Rationale} Expressing data at a granular level allows ultimate flexibility
for it to be sliced, diced, combined and aggregated. This capability to combine and
infer information is further enhanced by the use of \gls{property} definitions built on logic.
Having the properties themselves be objects that can be looked up means that all data
is self-defining and carries its meaning with it.
Since the information is self-defining there is no fixed schema for the \gls{ekgf}
as a whole and it can non-disruptively incorpate additional knowledge.

\paragraph{Implications} Some further discovery, with subject matter experts and
creators of source systems, is often needed to truly understand what a given
set of data really means and what can be inferred from it.
In other words you cannot rely on the name of a column in a spreadsheet.
A deceptively simple column name such as "number of European customers" leaves
open the meaning of "European" and "customer" and timing (when does one start
and stop being a customer?). And different sources could have different
interpretations of that same name.
The benefit is consistency, accuracy and the ability to make sound business decisions.

