%
% A.3.2 Enterprise Architecture -- Contribution to the EKG
%
An EKG could fulfil two different roles:

\begin{itemize}
    \item An \gls{ekg} could serve as a middleware technology offering the ability to integrate data across
          business processes, business units, etc.
          First, the business standards from an operating model may be useful to create business glossaries.
          Additionally, the integration requirements from an operating model will be used as a baseline to
          which a middleware \gls{ekg} has to comply.
          Furthermore, a core diagram may be useful to identify the different components and systems of
          the company that need to be reconciled, integrated, and coordinated.
          Finally, an operating model and core diagram could facilitate communication between business
          and \gls{ekg} developers.
    \item An \gls{ekg} could also serve as a more detailed representation of the enterprise than the core diagram.
          More specifically, an \gls{ekg} may allow business executives to conduct tailored and
          enterprise-wide analyses through computer inferencing and SPARQL-queries.
          For example, an \gls{ekg} may help business executives answers questions such as
          \textit{What age categories but the most popcorn in each state we operate in?} \textbf{TODO: Fix this} or
          \textit{Which of our end-to-end processes have the most delays?}.
          Therefore, a core diagram could serve as a high-level model to map out the things that the \gls{ekg}
          would later map out in much higher detail.
\end{itemize}


