Ontologies are the basis for Principle \Ref{sec:ekg-principle-meaning}\,---\,\Nameref{sec:ekg-principle-meaning}:

\somequote{%
    The meaning of every data point must be directly resolvable to a
    machine-readable definition in verifiable formal logic.%
}{EKGF}{https://www.ekgf.org/principles}

The link to precise meaning serves to mitigate problems created using the same word with multiple definitions;
and the challenges of expressing conceptual nuance using multiple informal sentences.
In the other direction, from ontology to vocabulary, it should be possible to generate a business glossary
directly from ontologies for a given scope.
Since they should capture the meaning of concepts applicable to an organization, or an even broader ecosystem,
the choice of concepts to include in an \gls{ekg} should be driven by business use cases.
And different overlapping ontologies may be included and mapped to cover different relevant aspects.
Likewise it should be possible to generate, and map to, models for more conventional tools from ontologies,
by applying technology-specific rules.

Semantic modeling also eliminates the problem of hard-coding assumptions about the world into a single data model.
And while multiple ontologies may coexist, they are able to be mapped and connected to each other.
In a mature environment, the data modeling process drives technology implementation,
by defining the detailed data structures and associated APIs.
These components (along with functional code) are included as part of the testing suite within the \gls{ekg} to
facilitate rapid deployment.

Different types of external data models are not needed in \gls{ekg} but can be mapped to or generated.
In fact, physical data modelers are a community with their own vocabulary.

Constraints/shapes for models are applied by context (use case)\,---\,there is no \glsfirst{svot}
for the \gls{ekg} as a whole.
Different ontologies may be used for different contexts and mapped to each other in the underlying knowledge graph.

Ontology elements are linked to by Vocabularies B2.2 and mapped to other Data Models B2.5 and Datasets B2.3 to
provide their meaning; and from Use Cases A3.x to provide their scope.
These aspects are covered by those respective capabilities.
