\section{Market Segmentation}\label{sec:ekg-mm-a-2-1}
\index{market segmentation}

The capability \enquote{Market Segmentation} is the ability to structurally recognize, define, manage and use the
company's market segments and drive decision making around products, services, sales and marketing operations.

\somequote{%
    Market segmentation is a marketing term that refers to aggregating prospective buyers into groups or segments
    with common needs and who respond similarly to a marketing action.
    Market segmentation enables companies to target different categories of consumers who perceive the full value
    of certain products and services differently from one another.
    \begin{itemize}
        \item Market segmentation seeks to identify targeted groups of consumers to tailor products and branding in a
              way that is attractive to the group.
        \item Markets can be segmented in several ways such as geographically, demographically, or behaviorally.
        \item Market segmentation helps companies minimize risk by figuring out which products are the most likely to
              earn a share of a target market and the best ways to market and deliver those products to the market.
        \item With risk minimized and clarity about the marketing and delivery of a product heightened,
              a company can then focus its resources on efforts likely to be the most profitable.
    \end{itemize}
}{Investopedia}{https://www.investopedia.com/terms/m/marketsegmentation.asp}

We welcome your input here.

\ekgmmContextSection

\ekgmmHowEKGRequiresThisCapability

Having the proper Market Segments defined will help with the selection, definition and prioritization of
the right use cases for the \gls{ekg}.

\ekgmmHowEKGAffectsThisCapability

The \gls{ekg} can bring all possible internal and external detail information about customers, products, services,
competition, sales volumes, customer requirements and many other details together forming a holistic and realistic,
almost real-time view of the position of the company in their markets.

We welcome your input here.


