\section[Operating Model]{Data-management \Glsfmttext{operating-model}}\label{sec:ekg-mm-b-4-1} % B.4.1 Operating Model

The people, processes, capabilities, and tools that define the role of data management in delivering value to an
organization’s customers.\footnote{%
    There is also a capability called ``\nameref{sec:ekg-mm-a-1-4}'' in the
    Business Pillar that has a different meaning, see \secref{sec:ekg-mm-a-1-4}.
}

The \gls{operating-model} can help stakeholders understand the complexity of the data manufacturing process and how
components relate to each other.
It specifies the roles and responsibilities of the stakeholders involved in the data management program.
It provides a framework and policies to help align governance concepts with operating requirements and
organizational culture.
An effective \gls{operating-model} can both describe the way the organization does business today (“as is”) and
communicate a vision of how an operation will work in the future (“to be”).

\ekgmmContextSection

The \gls{operating-model} for the \glsfirst{ekg:coe} establishes a new way of running the organization
to enable companies to accelerate development and operate more efficiently.
The \glsxtrshort{ekg} \iindex{governance framework}\index{\glsxtrshort{ekg}!governance framework} focuses on
combining new data capabilities (i.e. resolvable identity, standard ontologies, open standards)
as part of an integrated process.
A well defined \gls{operating-model} specifies architecture components that support flexible and reusable data to help
organizations achieve improvements in revenue, customer experience and cost.

\kgmmcorequestionssection

\begin{core-questions}

  \item [\thesection.1] Have the underlying principles (and challenges) of data management been established and
                        accepted by involved stakeholders
  \item [\thesection.2] Does the \gls{odm} have authority to enforce adherence to policy
  \item [\thesection.3] Has the data management funding model been established and implemented
  \item [\thesection.4] Has the organization identified and recruited stakeholders with sufficient skill sets to
                        implement the data management program
  \item [\thesection.5] Are involved stakeholders held accountable to data management program deliverables
  \item [\thesection.6] Has the organization defined and validated the \glspl{operating-model},
                        and workflows necessary to implement the data management program
  \item [\thesection.7] Are metrics and KPIs captured and actively used to improve the data management operating process
  \item [\thesection.8] Is the data management \gls{operating-model} audited for compliance and effectiveness

\end{core-questions}

