\section{Data Production \& Consumption}\label{sec:ekgmm-b-4-3} % B.4.3 Data Production Process

Data originates from a wide variety of business processes and flows through multiple systems before it is ingested into applications and analytical functions.
As data flows across this “chain of supply” - it can be renamed, enriched, transformed and updated (many times).
Data producers and consumers must work collaboratively to ensure that the data is fit for its intended purposes
This necessitates communications about the requirements for quality as well as an understanding of how the data is being used,
where it originates, how it has been transformed and its consistency with original intent.

\kgmmekgrationalesection

Management of the production/consumption process is one of the essential components of data management.
It is based in understanding what data is being exchanged and the ability to map dependencies and transformations (lineage).
The knowledge graph is the logical distribution point for data manufacturing - leveraging the ontology to ensure consistency of meaning across systems, people and processes.
The \glsxtrshort{ekg} is able to trace data flow and validate that defined use cases are aligned with agreed usage and obtained from authoritative sources.
Entitlements and redistribution rights are automatically tracked and fully auditable.
Data quality rules are linked to business vocabulary and structurally enforced across systems and processes to ensure consistency.

\kgmmcorequestionssection

\begin{core-questions}

  \item [\thesection.1] Is the data production/consumption process documented and verified from authoritative sources to consuming applications
  \item [\thesection.2] Are the requirements for data quality (and criticality) defined, verified and expressed as SLAs or other forms of data sharing agreement
  \item [\thesection.3] Is there an inventory of SLAs and is data production monitored against these agreements
  \item [\thesection.4] Is the data production/consumption process connected to ontologies and official business glossaries
  \item [\thesection.5] Are entitlements, permissions and authorizations tracked as data flows across systems
  \item [\thesection.6] Can data quality errors and deficiencies be traced back to where the data originated
  \item [\thesection.7] Are the data production/consumption governance processes in place and operational (ownership and accountability)

\end{core-questions}

