\section{Operating Model}\label{sec:ekgmm-b-4-1} % B.4.1 Operating Model

The people, processes, capabilities and tools that define the role of data management in delivering value to an
organization’s customers.
The operating model can help stakeholders understand the complexity of the data manufacturing process and how
components relate to each other.
It specifies the roles and responsibilities of the stakeholders involved in the data management program.
It provides a framework and policies to help align governance concepts with operating requirements and
organizational culture.
An effective operating model can both describe the way the organization does business today (“as is”) and
communicate a vision of how an operation will work in the future (“to be”).

\kgmmekgrationalesection

The operating model for the knowledge graph establishes a new way of running the organization to enable companies to
accelerate development and operate more efficiently.
The \glsxtrshort{ekg} governance framework focuses on combining new data capabilities (i.e. resolvable identity,
standard ontologies, open standards) as part of an integrated process.
A well defined operating model specifies architecture components that support flexible and reusable data to help
organizations achieve improvements in revenue, customer experience and cost.

\kgmmcorequestionssection

\begin{core-questions}

  \item [\thesection.1] Have the underlying principles (and challenges) of data management been established and
                        accepted by involved stakeholders
  \item [\thesection.2] Does the Office of Data Management have authority to enforce adherence to policy
  \item [\thesection.3] Has the data management funding model been established and implemented
  \item [\thesection.4] Has the organization identified and recruited stakeholders with sufficient skill sets to
                        implement the data management program
  \item [\thesection.5] Are involved stakeholders held accountable to data management program deliverables
  \item [\thesection.6] Has the organization defined and validated the operating models, and workflows necessary to
                        implement the data management program
  \item [\thesection.7] Are metrics and KPIs captured and actively used to improve the data management operating process
  \item [\thesection.8] Is the data management operating model audited for compliance and effectiveness

\end{core-questions}

