\section{Critical Data Elements}\label{sec:ekgmm-b-4-5} % B.4.5 Classification Management

\glsreset{cde}\Glspl{cde} are designated as having a material impact on a business process, regulatory report,
financial calculation or risk measure.
The designation of a data element as critical means it is important enough to be governed by organizational policy.
\Gls{cde} management is implemented as a negotiation process between producers and consumers that require
precision of meaning, understanding of data flow, capture of business rules and the management of quality based on
how the data will be used.
Many firms use the term \gls{cde} to describe various things such as data attributes, business concepts,
derived processes and physical expressions.
This confusion over nomenclature about concepts makes it difficult to distinguish granular data from how it is
assembled into business measures and how it is expressed in physical data repositories.

\ekgmmContextSection

In the \glsxtrshort{ekg}\improve[inline]{%
    We should be more explicit about this by saying that \glspl{cde}
    basically do not exist as such anymore, a data element is deemed critical from the point of view of the
    enterprise perhaps but that's just one viewpoint, one context.
    In the EKG we have to serve any viewpoint.
    For every use case there are data elements (concepts) that are critical which may be a whole
    different set of data elements than what enterprise level deems to be critical.
    All data elements are critical somewhere in some context.
    This has to do with the "single version of the truth delusion".
    It's of course fine to label certain data elements as "critical" but it should be tied to the use case.
    Data element X is critical for use case Y.},
\glsfmtlongpl{cde} are defined by data quality business rules and expressed as
machine-executable models.\improve{i.e. ontologies}
These rules are automatically executed across systems, processes and applications to ensure consistency.
Data is linked to the ontology and resolved to a single identifier to mitigate confusion about meaning when the
data is onboarded or transformed.
The \glsxtrshort{ekg} is able to trace data flow and verify that criticality is aligned with \glspl{sor}
and agreed usage.

\kgmmcorequestionssection

\begin{core-questions}

  \item [\thesection.1] Are critical data elements identified, verified and prioritized for specific
                        use cases and applications
  \item [\thesection.2] How is the organization managing the distinctions between granular data attributes and
                        derived/calculated business concepts
  \item [\thesection.3] Is the inventory of critical data elements implemented and linked to how the
                        data is being consumed
  \item [\thesection.4] Are critical business elements connected to business glossaries, ontologies,
                        \glspl{sor} and authorized distribution points
  \item [\thesection.5] Is the front-to-back flow of data defined, validated and linked to the designations of
                        critical data
  \item [\thesection.6] Are the governance mechanisms for managing critical data defined and operational

\end{core-questions}

