\bookmarksetup{bold=true, color=gray}
\part{Organization}\label{pt:ekgmm-d} % D Organization

The pillar "Organization" has the following components:

\begin{itemize}[leftmargin=.5in]
    \item [\ref{ch:ekgmm-d-1}] \nameref{ch:ekgmm-d-1}
    \item [\ref{ch:ekgmm-d-2}] \nameref{ch:ekgmm-d-2}
    \item [\ref{ch:ekgmm-d-3}] \nameref{ch:ekgmm-d-3}
    \item [\ref{ch:ekgmm-d-4}] \nameref{ch:ekgmm-d-4}
    \item [\ref{ch:ekgmm-d-5}] \nameref{ch:ekgmm-d-5}
\end{itemize}

\paragraph{Levels}

\begin{description}[nosep,font=\bfseries]

    \item [1. \glsfmtshort{ekg} Initiation, \glsfmtshort{mvp}]
    Champions are internal visionaries who have assembled a specialist team for implementation.
    The pilot is sanctioned and funded.
    Knowledge acceleration is being addressed.
    Overall organizational support is emerging

    \item [2. Extensible Platform (reusable components)]
    Operating model of collaboration is implemented to support the knowledge graph.
    The Center of Excellence and DataOps environment is initiated.
    Budget and implementation strategy are based on agile and synchronized with the
    use case tree methodology.

    \item [3. Enterprise Ready]
    The \gls{ekg} is recognized as a core service for the enterprise.
    Enterprise-wide ownership and funding processes are operational.
    The EKG Center of Excellence is a stand-alone production department.

\end{description}

\input{../../ekg-mm/sections/d-organization-1-executive-leadership.tex}
\input{../../ekg-mm/sections/d-organization-2-product-ownership.tex}
\input{../../ekg-mm/sections/d-organization-3-delivery-management.tex}
\input{../../ekg-mm/sections/d-organization-4-organizational-culture.tex}
\input{../../ekg-mm/sections/d-organization-5-organizational-capabilities.tex}