\section{The four capability-domains}\label{sec:the-four-capability-domains}
\index{capability domain}

All capabilities that we measure in the \gls{ekgmm}\footnote{See \cite{ekgmm}} are categorized
in four major categories\,---\,also called "pillars"\,---\,that match the four primary audiences that are involved:

The Business (Strategy) is leading.
In a "\iindex{Data-centric}" organization, \iindex{Data Strategy} comes second and fully supports the
Business Strategy\index{business!strategy}.
Then derived from that we have a supporting and facilitating Technology and Organizational Strategy.
\index{strategy!business strategy}
\index{strategy!data strategy}
\index{strategy!technology strategy}
\index{strategy!organization strategy}

The four capability domains roughly correspond with the four primary audiences that we are addressing:

\begin{enumerate}
    \item The audience of people on the business-side
    \item The audience of people in the data-management and data-governance departments
    \item The audience of technologists
    \item The audience of people that are neither business, data nor tech.
\end{enumerate}

\subsection{Capability Domain: Business}

All Business-side capabilities including \myuline{\nameref{ch:ekg-mm-business-strategy-actuation}},
\index{business!strategy} \nameref{ch:ekg-mm-business-architecture-elaboration},
\index{business!architecture!elaboration} \nameref{ch:ekg-mm-business-enablers}, Alignment,
\nameref{sec:ekg-mm-business-operating-model} and others.
Does not include all the actual Business Capabilities \index{business!capabilities} that
an enterprise may have themselves.

Addresses the audience of personas on the business-side of an enterprise, C-level, LOB execs, corporate planners,
business architects, product owners, management consultants and so forth.

\subsection{Capability Domain: Data}

All Data (Management) capabilities including \myuline{\nameref{ch:ekg-mm-data-strategy}}.

Addresses the audience of people in the data-management and data-governance departments.

\subsection{Capability Domain: Technology}

All Technology Capabilities including \myuline{Technology Strategy}.

Addresses the audience of technologists, technical architects, developers, infrastructure execs and experts,
security execs and experts etc.

\subsection{Capability Domain: Organization}

All relevant Organizational Capabilities including \myuline{Organizational Strategy}

Addresses the audience of people that are neither business, data nor tech such as financial execs and experts, risk
execs and experts, program/portfolio/project managers, HR execs and experts and so forth.

