\bookmarksetup{bold=true, color=blue}
\part{Data}\label{pt:ekgmm-b} % B Data

The pillar "Data" has the following components:

\begin{itemize}[leftmargin=.5in]
  \item [\ref{ch:ekg-mm-b-1}] \nameref{ch:ekg-mm-b-1}
  \item [\ref{ch:ekg-mm-b-2}] \nameref{ch:ekg-mm-b-2}
  \item [\ref{ch:ekg-mm-b-3}] \nameref{ch:ekg-mm-b-3}
  \item [\ref{ch:ekg-mm-b-4}] \nameref{ch:ekg-mm-b-4}
\end{itemize}

\paragraph{Levels}

\begin{description}[nosep,font=\bfseries]

    \item [1. \ekgmmLevelOneLabel]
    Core data management capabilities (\gls{operating-model}, inventory, data architecture,
    \hyperref[sec:ekg-mm-business-terminology]{business glossary or terminology},
    pipeline management, etc.) are being performed.
    Specific use cases are being implemented with specialist teams for the pilot initiative.
    
    \item [2. \ekgmmLevelTwoLabel]
    Critical data elements are prioritized in the ontology.
    Approach to identity and meaning resolution is established.
    Use case trees are defined and modeled to capture shared data relationships.
    The knowledge graph is becoming the central point for integration.

    \item [3. \ekgmmLevelThreeLabel]
    Inventory is embedded into the \gls{ekg} and linked to governance.
    Data is expressed as formal ontologies, onboarded into the \gls{ekg} and searchable.
    Data flows are defined and modeled.
    The \gls{ekg} is the authoritative source for data.

\end{description}

\input{../../ekg-mm/chapters/b-1-data-strategy.tex}
\input{../../ekg-mm/chapters/b-2-data-architecture.tex}
\input{../../ekg-mm/chapters/b-3-data-quality.tex}
\input{../../ekg-mm/chapters/b-4-data-governance.tex}
