\bookmarksetup{bold=true, color=yellow}
\part{Technology}\label{pt:ekgmm-c} % C Technology

The pillar "Technology" has the following components:

\begin{itemize}[leftmargin=.5in]
    \item [\ref{ch:ekg-mm-c-1}] \nameref{ch:ekg-mm-c-1}
    \item [\ref{ch:ekg-mm-c-2}] \nameref{ch:ekg-mm-c-2}
    \item [\ref{ch:ekg-mm-c-3}] \nameref{ch:ekg-mm-c-3}
\end{itemize}

\paragraph{Levels}

\begin{description}[nosep,font=\bfseries]

    \item [1. \ekgmmLevelOneLabel]
    Technology strategy is focused on experimentation and innovation.
    Manual data transformation and targeted \gls{etl} is underway for the pilot.
    Limited infrastructure and dedicated efforts to build initial knowledge graph components.

    \item [2. \ekgmmLevelTwoLabel]
    Reusable architecture based on expanded design principles.
    Core software development design approaches are being established and incorporated
    into strategy.
    \gls{cto} focuses on extending pilot initiatives for additional leverage.

    \item [3. \ekgmmLevelThreeLabel]
    Commitment to the \gls{ekg} as the strategic infrastructure for the organization.
    \gls{iac} and continuous deployment adopted and implemented.
    Cloud architecture defined for elasticity.
    Datapoint security and authentication processes implemented

\end{description}

\input{../../ekg-mm/chapters/c-technology-1-technology-strategy.tex}
\input{../../ekg-mm/chapters/c-technology-2-technology-execution.tex}
\input{../../ekg-mm/chapters/c-technology-3-user-experience.tex}
