\chapter{Manifesto}\label{ch:ekg-manifesto}

TODO -- this is just a very early first stab at it with some random points.

All data will be connected.

All data will be made available anywhere (within entitlement limits) at any time to any device, node or edge.

Any data source will be turned into a data publisher or supplier of one or more datasets.

Any data sink will be turned into a data consumer (of one or more datasets).

Data suppliers and consumers will find each other via a data market using a standard "lingua franca" for the
data itself, its meaning, all its associated policies and metadata and especially also its use cases as executable
models.

The data market manages the information supply chains between all the various suppliers and consumers.

The global data market will consist of many other more specific data markets e.g. per industry or per enterprise.

An \gls{ekg} is the combination of one or more data markets and the deployment of its use cases.

For any given object there may be many representations in many datasets.
These representations may be different in shape, meaning, timeliness, relevance and quality\,---\,i.e.
any given representation of information about a given object may represent a
different version of the truth.

All representations of any given object shall be linked via shared identifiers.

Any given object consists of 1 or more datapoints, where each datapoint represents a logical property of the given
object with potentially multiple versions of the truth in terms of meaning, timeliness, relevance and quality.

Any representation for any given \gls{data-point} of any data source shall be made available to any device,
node or edge in the network within legal, policy and entitlement limits in real-time.

Every "object" that is represented as data in whichever dataset anywhere, shall have an identifier that is universally
unique, permanent, meaningless or opaque and therefore shareable, resolvable through the HTTP protocol.
See \ref{sec:ekg-principles-identity}~\nameref{sec:ekg-principles-identity}.

